References

### 2015-03-28 cv/XieXiaolei-Analyst.tex
Revise my CV as an analyst.

\section*{My Goal}
A self-funded Ph.D student of Finance \& Insurance mathematics
at KU, who is very experienced in programming and statistical analysis, is
looking for a part-time job as a quantitative analyst.

\section*{Education}
\begin{itemize}
\item Ph.D of Finance \& Insurance Mathematics, October 2014 - present
  \begin{itemize}
    \item {\it Reseach Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      of samples with heavy-tails. The purpose is dimension
      reduction, by which the behaviour of a diverse portfolio is
      replicated by one with much few components and hence analysis of
      the portfolio becomes more simplified and focused.

@@

\section*{Language Skills}
\begin{itemize}
\item English: Fluent
\item Swedish: Fairly good
\item Danish: Beginner
\end{itemize}

>>>>

% \section*{My Goal}
% A PhD student of Finance \& Insurance Mathematics at Copenhagen
% University, who is very experienced in programming and statistical
% analysis,
% % is looking for a part-time job as a quantitative analyst.
% is looking for a summer internship as a quantitative analyst.

\section*{Education}
\begin{itemize}
\item PhD of Finance \& Insurance Mathematics, Copenhagen University,
  October 2014 - present
  \begin{itemize}
    \item {\it Research Areas:} I am mainly interested in the
      determination of the largest eigenvalues of a covariance matrix
      of samples with heavy-tails. The purpose is dimension
      reduction, by which the behavior of a large portfolio is
      replicated by one with much fewer components and hence analysis of
      the portfolio can be more simplified and focused.

@@

\section*{Programming Skills}
\begin{table}[htb!]
  \centering
  \begin{tabular}{|l|c|| l |c|}
    \hline
    Skill & Experience (years) & Skill & Experience (years) \\
    \hline
    Matlab & 4.5 & R & 0.5 \\
    C & 10 & C++ & 3 \\
    SQL & 3 & Java & 3 \\
    Python & 1 &&\\
    \hline
  \end{tabular}
\end{table}

% \section*{Language Skills}
% \begin{itemize}
% \item English: Fluent
% \item Swedish: Fairly good
% \item Danish: Beginner
% \end{itemize}
